Ethereum: A Secure Decentralised Generalised Transaction Ledger

### 2014-04-07 Paper.tex
Fixes.

Transparency. Open state. User can be guaranteed that backend will do what front-end says it will. Parties can analyse and be wholly confident in outcomes given events.

@@

The other two components in the block are simply a list of the transactions (as defined previously) and a list of uncle block headers (of the same format as above). Formally, we can refer to a block $B$:
\begin{equation}
B \equiv (H, \mathbf{T}, \mathbf{U})
\end{equation}

@@

We define $P(B_H)$ to be the parent block of $B$, formally:
\begin{equation}
P(H) \equiv B': S(R(B')) = H_p
\end{equation}

@@

We define the creation function formally as the function $\Lambda$, which evaluates from these values, together with the state $\mathbb{S}_0$ to the tuple containing the new state, additional database entries and remaining gas $(\mathbb{S}_P, g')$, as in \ref{ch:transactions}:

\begin{equation}
(\mathbb{S}_P, g') \equiv \Lambda(\mathbb{S}_0, s, o, g, p, v, \mathbf{i}, \mathbf{b})
\end{equation}

The address of the new contract is defined as being the rightmost 160 bits of the SHA3 hash of RLP encoding of the structure \texttt{[ sender, nonce ]}. In the unlikely event that the address is already in use, it is treated as a big-endian integer and incremented by one until an unused address is arrived at. Thus we define the creation address function $A$:

\begin{eqnarray}
A(s, o) & \equiv & a \quad \text{where:} \\
a & = & \arg \min_x : x \geqslant a' \wedge \mathbb{S}_0[x] = \varnothing \\
a' & = & \mathcal{B}_{96..255}(\mathcal{S}(\mathcal{R}([s, o])))
\end{eqnarray}

where $\mathcal{S}$ is the SHA3 256-bit hash function, $\mathcal{R}$ is the RLP encoding function, $\mathcal{B}_{a..b}(X)$ evaluates to binary value containing the bits of indices in the range $[a, b]$ of the binary data $X$ and $\mathbb{S}_0[x]$ is the address state of $x$ or $\varnothing$ if none exists.

The account's nonce is initially defined as zero, the balance as the value passed, the storage as empty and the code hash as the SHA3 256-bit hash of the code, thus the mutated state becomes $\mathbb{S}^*$:

\begin{eqnarray}
\mathbb{S}^* & \equiv & \mathbb{S} \quad \text{except:} \\
\mathbb{S}^*[A(s, o)] & \equiv & ( 0, v, \varnothing, \mathcal{S}(\mathbf{b}) )
\end{eqnarray}

@@

If such an exception does not occur, then the remaining gas is refunded to the originator and the now-altered state is allowed to persevere. Thus formally, we may specify the new state and gas as $\mathbb{S}'$, $g'$ where:

\begin{eqnarray}
(\mathbb{S}^{**}, g') & \equiv & \Xi(\mathbb{S}^*, g, I) \\
\mathbb{S}_P & \equiv & \begin{cases}
\mathbb{S}_0 & \text{if} \quad \mathbb{S}^{**} = \varnothing \\
\mathbb{S}^{**} & \text{otherwise}
\end{cases} \\
I_a & \equiv & a \\
I_o & \equiv & s \\
I_p & \equiv & p \\
I_\mathbf{d} & \equiv & [] \\
I_s & \equiv & s \\
I_v & \equiv & v \\
I_\mathbf{b} & \equiv & \mathbf{i}
\end{eqnarray}

@@

In the case of executing a message call, several parameters are required: sender ($s$), transaction originator ($o$), recipient ($r$), available gas ($g$), value ($v$) and gas price ($p$) together with an arbitrary length byte array, $\mathbf{d}$, the input data of the call. Aside from evaluating to a new state and additional database entries, message calls also have an extra component---the output data denoted by the byte array $\mathbf{o}$. This is ignored when executing transactions, however message calls can be initiated due to VM-code execution and in this case this information is used.

\begin{equation}
(\mathbb{S}_P, g', \mathbf{o}) \equiv \Theta(\mathbb{S}, s, o, r, g, p, v, \mathbf{d})
\end{equation}

We define $\mathbb{S}_1$, the rollback state as the original state but with the value transferred to the recipient:

\begin{eqnarray}
\mathbb{S}_1 & \equiv & \mathbb{S} \quad \text{except:} \\
\mathbb{S}_1[r]_{balance} & \equiv & \mathbb{S}_1[r]_{balance} + v
\end{eqnarray}

If the recipient account contains no code to be executed (i.e. it's not a contract), then we define the final state as being equivalent to the rollback state. In the case that the recipient contains code to be executed (i.e. that the account is a contract), then the contract's body code (identified as the fragment whose SHA3 hash is $\mathbb{S}[r]_{code}]$) is executed according to the execution model (see section \ref{ch:model}). Just as with contract creation, if the execution halts due to an exhausted gas supply, then no gas is refunded to the caller and the state is reverted to the point immediately prior to code execution.

\begin{eqnarray}
\mathbb{S}' & \equiv & \begin{cases}
\mathbb{S}_1 & \text{if} \quad \mathbb{S}_1[r]_{code} = \varnothing \\
\mathbb{S}_1 & \text{if} \quad \mathbb{S}^{**} = \varnothing \\
\mathbb{S}^{**} & \text{otherwise}
\end{cases} \\
(\mathbb{S}^{**}, g', \mathbf{o}) & \equiv & \Xi(\mathbb{S}_1, g, I) \\
I_a & \equiv & a \\
I_o & \equiv & o \\
I_p & \equiv & p \\
I_\mathbf{d} & \equiv & \mathbf{d} \\
I_s & \equiv & s \\
I_v & \equiv & v \\
\text{Let} \quad \mathcal{S}(I_\mathbf{b}) & = & \mathbb{S}[r]_{code}
\end{eqnarray}

@@

We define the block reward as 1500 Finney:
\begin{equation}
\text{Let} \quad R_b = 1.5^{16}
\end{equation}

@@

\begin{tabular*}{\columnwidth}[h]{rlrrl}
\toprule
\multicolumn{5}{c}{\textbf{20s: SHA3}} \vspace{5pt} \\
\textbf{Value} & \textbf{Mnemonic} & $\delta$ & $\alpha$ & \textbf{Description} \vspace{5pt} \\
0x20 & {\small SHA3} & 2 & 1 & Compute SHA3-256 hash. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathcal{S}(\mathbb{M}_M[ \mathbb{M}_S[0] \dots (\mathbb{M}_S[0] + \mathbb{M}_S[1] - 1) ])$ \\
&&&& $\mathbb{M}'_i \equiv \max(\mathbb{M}_i, \ceil{ (\mathbb{M}_S[0] + \mathbb{M}_S[1] - 1) \div 32 })$ \\
\bottomrule
\end{tabular*}

\begin{tabular*}{\columnwidth}[h]{rlrrl}
\toprule
\multicolumn{5}{c}{\textbf{30s: Environmental Information}} \vspace{5pt} \\
\textbf{Value} & \textbf{Mnemonic} & $\delta$ & $\alpha$ & \textbf{Description} \vspace{5pt} \\
0x30 & {\small ADDRESS} & 0 & 1 & Get address of currently executing account. \\
&&&& $\mathbb{M}'_T[0] \equiv I_a$ \\
\midrule
0x31 & {\small BALANCE} & 0 & 1 & Get balance of currently executing account. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{S}[I_a]_{balance}$ \\
\midrule
0x32 & {\small ORIGIN} & 0 & 1 & Get execution origination address. \\
&&&& $\mathbb{M}'_T[0] \equiv I_o$ \\
&&&& This is the sender of original transaction; it's never a contract. \\
\midrule
0x33 & {\small CALLER} & 0 & 1 & Get caller address. \\
&&&& $\mathbb{M}'_T[0] \equiv I_c$ \\
&&&& This is the address of the account that is directly responsible for this execution. \\
\midrule
0x34 & {\small CALLVALUE} & 0 & 1 & Get deposited value by the instruction/transaction responsible for this execution. \\
&&&& $\mathbb{M}'_T[0] \equiv I_v$ \\
\midrule
0x35 & {\small CALLDATALOAD} & 1 & 1 & Get input data of current environment. \\
&&&& $\mathbb{M}'_T[0] \equiv I_\mathbf{d}[ \mathbb{M}_S[0] \dots (\mathbb{M}_S[0] + 31) ]$ \\
&&&& This pertains to the input data passed with the message call instruction or transaction. \\
\midrule
0x36 & {\small CALLDATASIZE} & 0 & 1 & Get size of input data in current environment. \\
&&&& $\mathbb{M}'_T[0] \equiv \lVert I_\mathbf{d} \rVert$ \\
&&&& This pertains to the input data passed with the message call instruction or transaction. \\
\midrule
0x37 & {\small GASPRICE} & 0 & 1 & Get price of gas in current environment. \\
&&&& $\mathbb{M}'_T[0] \equiv I_p$ \\
&&&& This is gas price specified by the originating transaction.\\
\bottomrule
\end{tabular*}

@@

\begin{tabular*}{\columnwidth}[h]{rlrrl}
\toprule
\multicolumn{5}{c}{\textbf{50s: Stack, Memory, Storage and Flow Operations}} \vspace{5pt} \\
\textbf{Value} & \textbf{Mnemonic} & $\delta$ & $\alpha$ & \textbf{Description} \vspace{5pt} \\
0x50 & {\small POP} & 1 & 0 & Remove item from stack. \\
\midrule
0x51 & {\small DUP} & 1 & 2 & Duplicate stack item. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{M}_S[0]$ \\
\midrule
0x52 & {\small SWAP} & 2 & 2 & Exchange stack items. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{M}_S[1]$ \\
&&&& $\mathbb{M}'_T[1] \equiv \mathbb{M}_S[0]$ \\
\midrule
0x53 & {\small MLOAD} & 1 & 1 & Load word from memory. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{M}_M[\mathbb{M}_S[0] \dots (\mathbb{M}_S[0] + 31) ]$ \\
&&&& $\mathbb{M}'_i \equiv \max(\mathbb{M}_i, \ceil{ (\mathbb{M}_S[0] + 31) \div 32 })$ \\
\midrule
0x54 & {\small MSTORE} & 2 & 0 & Save word to memory. \\
&&&& $\mathbb{M}'_M[ \mathbb{M}_S[0] \dots (\mathbb{M}_S[0] + 31) ] \equiv \mathbb{M}_S[1]$ \\
&&&& $\mathbb{M}'_i \equiv \max(\mathbb{M}_i, \ceil{ (\mathbb{M}_S[0] + 31) \div 32 })$ \\
\midrule
0x55 & {\small MSTORE8} & 2 & 0 & Save byte to memory. \\
&&&& $\mathbb{M}'_M[ \mathbb{M}_S[0] ] \equiv (\mathbb{M}_S[1] \mod 256) $ \\
&&&& $\mathbb{M}'_i \equiv \max(\mathbb{M}_i, \ceil{ \mathbb{M}_S[0] \div 32 })$ \\
\midrule
0x56 & {\small SLOAD} & 1 & 1 & Load word from storage. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{S}'[I_a]_{storage}[\mathbb{M}_S[0]]$ \\
\midrule
0x57 & {\small SSTORE} & 2 & 0 & Save word to storage. \\
&&&& $\mathbb{S}'[I_a]_{storage}[ \mathbb{M}_S[0] ] \equiv \mathbb{M}_S[1] $ \\
&&&& $c_{\text{\tiny SSTORE}} \equiv \begin{cases}
2G_{sstore} & \text{if} \quad \mathbb{M}_S[1] \neq 0 \; \wedge \; \mathbb{S}[I_a]_{storage}[\mathbb{M}_S[0]] = 0 \\
0 & \text{if} \quad \mathbb{M}_S[1] = 0 \; \wedge \; \mathbb{S}[I_a]_{storage}[\mathbb{M}_S[0]] \neq 0 \\
G_{sstore} & \text{otherwise}
\end{cases}$ \\
\midrule
0x58 & {\small JUMP} & 1 & 0 & Alter the program counter. \\
&&&& $J_{\text{\tiny JUMP}}(\mathbb{M}) \equiv \mathbb{M}_S[0] $ \\
&&&& This has the effect of writing said value to $\mathbb{M}_{pc}$. See section \ref{ch:model}. \\
\midrule
0x59 & {\small JUMPI} & 2 & 0 & Conditionally alter the program counter. \\
&&&& $J_{\text{\tiny JUMPI}}(\mathbb{M}) \equiv \begin{cases} \mathbb{M}_S[0] & \text{if} \quad \mathbb{M}_S[0] = 0 \\ \mathbb{M}_{pc} + 1 & \text{otherwise} \end{cases} $ \\
&&&& This has the effect of writing said value to $\mathbb{M}_{pc}$. See section \ref{ch:model}. \\
\midrule
0x5a & {\small PC} & 0 & 1 & Get the program counter. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{M}_{pc}$ \\
\midrule
0x5b & {\small MSIZE} & 0 & 1 & Get the size of active memory. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{M}_{i}$ \\
\midrule
0x5c & {\small GAS} & 0 & 1 & Get the amount of available gas. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{M}_{g}$ \\
\bottomrule
\end{tabular*}

@@

\begin{tabular*}{\columnwidth}[h]{rlrrl}
\toprule
\multicolumn{5}{c}{\textbf{f0s: System operations}} \vspace{5pt} \\
\textbf{Value} & \textbf{Mnemonic} & $\delta$ & $\alpha$ & \textbf{Description} \vspace{5pt} \\
0xf0 & {\small CREATE} & 5 & 1 & Create a new contract. \\
&&&& $\mathbf{b} \equiv \mathbb{M}_M[ \mathbb{M}_S[1] \dots (\mathbb{M}_S[1] + \mathbb{M}_S[2] - 1) ]$ \\
&&&& $\mathbf{i} \equiv \mathbb{M}_M[ \mathbb{M}_S[3] \dots (\mathbb{M}_S[3] + \mathbb{M}_S[4] - 1) ]$ \\
&&&& $(\mathbb{S}', \mathbb{M}'_g) \equiv \Lambda(\mathbb{S}, I_a, I_o, \mathbb{M}_g, I_p, \mathbb{M}_S[0], \mathbf{i}, \mathbf{b})$ \\
&&&& $\mathbb{M}'_T[0] \equiv x$ \\
&&&& where $x=0$ if the code execution for this operation failed due to lack of gas;\\
&&&& $x=A(I_a, \mathbb{S}[I_a]_{nonce})$, the address of the newly created contract, otherwise. \\
&&&& $\mathbb{M}'_i \equiv \max(\mathbb{M}_i, \ceil{ \max(\mathbb{M}_S[1] + \mathbb{M}_S[2] - 1, \mathbb{M}_S[3] + \mathbb{M}_S[4] - 1) \div 32 })$ \\
\midrule
0xf1 & {\small CALL} & 7 & 1 & Message-call into contract. \\
&&&& $\mathbf{i} \equiv \mathbb{M}_M[ \mathbb{M}_S[3] \dots (\mathbb{M}_S[3] + \mathbb{M}_S[4] - 1) ]$ \\
&&&& $\mathbf{o} \equiv \mathbb{M}_M[ \mathbb{M}_S[5] \dots (\mathbb{M}_S[5] + \mathbb{M}_S[6] - 1) ]$ \\
&&&& Let $g_k = \begin{cases}0 & \text{if} \quad \mathbb{M}_S[2] = 0 \\ \mathbb{M}_g - \min(\mathbb{M}_g, \mathbb{M}_S[2]) & \text{otherwise} \end{cases}$ \\
&&&& $(\mathbb{S}', g', \mathbf{o}) \equiv \Theta(\mathbb{S}, I_a, I_o, \mathbb{M}_S[0], g, I_p, \mathbb{M}_g - g_k, \mathbb{M}_S[1], \mathbf{i})$ \\
&&&& $\mathbb{M}'_g \equiv g' + g_k$ \\
&&&& $\mathbb{M}'_T[0] \equiv x$ \\
&&&& where $x=0$ if the code execution for this operation failed due to lack of gas;\\
&&&& $x=1$ otherwise. \\
&&&& $\mathbb{M}'_i \equiv \max(\mathbb{M}_i, \ceil{ \max(\mathbb{M}_S[3] + \mathbb{M}_S[4] - 1, \mathbb{M}_S[5] + \mathbb{M}_S[6] - 1) \div 32 })$ \\
\midrule
0xf2 & {\small RETURN} & 2 & 0 & Halt execution returning output data. \\
&&&& $H_{\text{\tiny RETURN}}(\mathbb{M}) \equiv \mathbb{M}_M[ \mathbb{M}_S[0] \dots ( \mathbb{M}_S[0] + \mathbb{M}_S[1] - 1 ) ]$ \\
&&&& This has the effect of halting the execution at this point with output defined.\\
&&&& See section \ref{ch:model}. \\
&&&& $\mathbb{M}'_i \equiv \max(\mathbb{M}_i, \ceil{ (\mathbb{M}_S[0] + \mathbb{M}_S[1] - 1) \div 32 })$ \\
\midrule
0xff & {\small SUICIDE} & 1 & 0 & Halt execution and obliterate account. \\
&&&& $\mathbb{S}'[\mathbb{M}_S[0]]_{balance} \equiv \mathbb{S}[\mathbb{M}_S[0]]_{balance} + \mathbb{S}[I_a]_{balance}$ \\
&&&& $\mathbb{S}'[I_a] \equiv \varnothing$ \\
\bottomrule
\end{tabular*}

@@

$z_{256}$ refers to the parent hash, a 256-bit hash which is all zeroes.

>>>>

Incorruptability of judgement. Transparency. Open state. User can be guaranteed that backend will do what front-end says it will. Parties can analyse and be wholly confident in outcomes given events.

@@

The other two components in the block are simply a list of uncle block headers (of the same format as above) and a list of the transactions (as defined previously). Formally, we can refer to a block $B$:
\begin{equation}
B \equiv (H, \mathbf{U}, \mathbf{T})
\end{equation}

@@

We define $P(B_H)$ to be the parent block of $B$, formally:
\begin{equation}
P(H) \equiv B': \mathcal{S}(\mathcal{R}(B')) = H_p
\end{equation}

@@

We define the creation function formally as the function $\Lambda$, which evaluates from these values, together with the state $\mathbb{S}_0$ to the tuple containing the new state, additional database entries and remaining gas $(\mathbb{S}_P, g')$, as in \ref{ch:transactions}:
\begin{equation}
(\mathbb{S}_P, g') \equiv \Lambda(\mathbb{S}_0, s, o, g, p, v, \mathbf{i}, \mathbf{b})
\end{equation}

The address of the new contract is defined as being the rightmost 160 bits of the SHA3 hash of RLP encoding of the structure \texttt{[ sender, nonce ]}. In the unlikely event that the address is already in use, it is treated as a big-endian integer and incremented by one until an unused address is arrived at. Thus we define the creation address function $A$:
\begin{eqnarray}
A(s, n) & \equiv & a \quad \text{where:} \\
a & = & \arg \min_x : x \geqslant a' \wedge \mathbb{S}_0[x] = \varnothing \\
a' & = & \mathcal{B}_{96..255}(\mathcal{S}(\mathcal{R}([s, n])))
\end{eqnarray}

where $\mathcal{S}$ is the SHA3 256-bit hash function, $\mathcal{R}$ is the RLP encoding function, $\mathcal{B}_{a..b}(X)$ evaluates to binary value containing the bits of indices in the range $[a, b]$ of the binary data $X$ and $\mathbb{S}_0[x]$ is the address state of $x$ or $\varnothing$ if none exists. Note we use one fewer than the sender's nonce value; we assert that we have incremented the sender account's nonce prior to this call, and so the value used is the sender's nonce at the beginning of the responsible transaction or VM operation.

The account's nonce is initially defined as zero, the balance as the value passed, the storage as empty and the code hash as the SHA3 256-bit hash of the code, thus the mutated state becomes $\mathbb{S}^*$:
\begin{eqnarray}
\mathbb{S}^* & \equiv & \mathbb{S} \quad \text{except:} \\
\mathbb{S}^*[A(s, \mathbb{S}[s]_{nonce})] & \equiv & ( 0, v, \varnothing, \mathcal{S}(\mathbf{b}) )
\end{eqnarray}

@@

If such an exception does not occur, then the remaining gas is refunded to the originator and the now-altered state is allowed to persevere. Thus formally, we may specify the new state and gas as $\mathbb{S}'$, $g'$ where:
\begin{eqnarray}
(\mathbb{S}^{**}, g') & \equiv & \Xi(\mathbb{S}^*, g, I) \\
\mathbb{S}_P & \equiv & \begin{cases}
\mathbb{S}_0 & \text{if} \quad \mathbb{S}^{**} = \varnothing \\
\mathbb{S}^{**} & \text{otherwise}
\end{cases} \\
I_a & \equiv & a \\
I_o & \equiv & s \\
I_p & \equiv & p \\
I_\mathbf{d} & \equiv & [] \\
I_s & \equiv & s \\
I_v & \equiv & v \\
I_\mathbf{b} & \equiv & \mathbf{i}
\end{eqnarray}

@@

In the case of executing a message call, several parameters are required: sender ($s$), transaction originator ($o$), recipient ($r$), available gas ($g$), value ($v$) and gas price ($p$) together with an arbitrary length byte array, $\mathbf{d}$, the input data of the call. Aside from evaluating to a new state and additional database entries, message calls also have an extra component---the output data denoted by the byte array $\mathbf{o}$. This is ignored when executing transactions, however message calls can be initiated due to VM-code execution and in this case this information is used.
\begin{equation}
(\mathbb{S}_P, g', \mathbf{o}) \equiv \Theta(\mathbb{S}, s, o, r, g, p, v, \mathbf{d})
\end{equation}

We define $\mathbb{S}_1$, the rollback state as the original state but with the value transferred to the recipient:
\begin{eqnarray}
\mathbb{S}_1 & \equiv & \mathbb{S} \quad \text{except:} \\
\mathbb{S}_1[r]_{balance} & \equiv & \mathbb{S}_1[r]_{balance} + v
\end{eqnarray}

If the recipient account contains no code to be executed (i.e. it's not a contract), then we define the final state as being equivalent to the rollback state. In the case that the recipient contains code to be executed (i.e. that the account is a contract), then the contract's body code (identified as the fragment whose SHA3 hash is $\mathbb{S}[r]_{code}]$) is executed according to the execution model (see section \ref{ch:model}). Just as with contract creation, if the execution halts due to an exhausted gas supply, then no gas is refunded to the caller and the state is reverted to the point immediately prior to code execution.
\begin{eqnarray}
\mathbb{S}' & \equiv & \begin{cases}
\mathbb{S}_1 & \text{if} \quad \mathbb{S}_1[r]_{code} = \varnothing \\
\mathbb{S}_1 & \text{if} \quad \mathbb{S}^{**} = \varnothing \\
\mathbb{S}^{**} & \text{otherwise}
\end{cases} \\
(\mathbb{S}^{**}, g', \mathbf{o}) & \equiv & \Xi(\mathbb{S}_1, g, I) \\
I_a & \equiv & a \\
I_o & \equiv & o \\
I_p & \equiv & p \\
I_\mathbf{d} & \equiv & \mathbf{d} \\
I_s & \equiv & s \\
I_v & \equiv & v \\
\text{Let} \quad \mathcal{S}(I_\mathbf{b}) & = & \mathbb{S}[r]_{code}
\end{eqnarray}

@@

We define the block reward as 1500 Finney:
\begin{equation}
\text{Let} \quad R_b = 1.5 * 10^{16}
\end{equation}

@@

\begin{tabular*}{\columnwidth}[h]{rlrrl}
\toprule
\multicolumn{5}{c}{\textbf{20s: SHA3}} \vspace{5pt} \\
\textbf{Value} & \textbf{Mnemonic} & $\delta$ & $\alpha$ & \textbf{Description} \vspace{5pt} \\
0x20 & {\small SHA3} & 2 & 1 & Compute SHA3-256 hash. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathcal{S}(\mathbb{M}_M[ \mathbb{M}_S[0] \dots (\mathbb{M}_S[0] + \mathbb{M}_S[1] - 1) ])$ \\
&&&& $\mathbb{M}'_i \equiv \max(\mathbb{M}_i, \ceil{ (\mathbb{M}_S[0] + \mathbb{M}_S[1]) \div 32 })$ \\
\bottomrule
\end{tabular*}

\begin{tabular*}{\columnwidth}[h]{rlrrl}
\toprule
\multicolumn{5}{c}{\textbf{30s: Environmental Information}} \vspace{5pt} \\
\textbf{Value} & \textbf{Mnemonic} & $\delta$ & $\alpha$ & \textbf{Description} \vspace{5pt} \\
0x30 & {\small ADDRESS} & 0 & 1 & Get address of currently executing account. \\
&&&& $\mathbb{M}'_T[0] \equiv I_a$ \\
\midrule
0x31 & {\small BALANCE} & 0 & 1 & Get balance of currently executing account. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{S}[I_a]_{balance}$ \\
\midrule
0x32 & {\small ORIGIN} & 0 & 1 & Get execution origination address. \\
&&&& $\mathbb{M}'_T[0] \equiv I_o$ \\
&&&& This is the sender of original transaction; it's never a contract. \\
\midrule
0x33 & {\small CALLER} & 0 & 1 & Get caller address. \\
&&&& $\mathbb{M}'_T[0] \equiv I_c$ \\
&&&& This is the address of the account that is directly responsible for this execution. \\
\midrule
0x34 & {\small CALLVALUE} & 0 & 1 & Get deposited value by the instruction/transaction responsible for this execution. \\
&&&& $\mathbb{M}'_T[0] \equiv I_v$ \\
\midrule
0x35 & {\small CALLDATALOAD} & 1 & 1 & Get input data of current environment. \\
&&&& $\mathbb{M}'_T[0] \equiv I_\mathbf{d}[ \mathbb{M}_S[0] \dots (\mathbb{M}_S[0] + 32) ]$ \\
&&&& This pertains to the input data passed with the message call instruction or transaction. \\
\midrule
0x36 & {\small CALLDATASIZE} & 0 & 1 & Get size of input data in current environment. \\
&&&& $\mathbb{M}'_T[0] \equiv \lVert I_\mathbf{d} \rVert$ \\
&&&& This pertains to the input data passed with the message call instruction or transaction. \\
\midrule
0x37 & {\small GASPRICE} & 0 & 1 & Get price of gas in current environment. \\
&&&& $\mathbb{M}'_T[0] \equiv I_p$ \\
&&&& This is gas price specified by the originating transaction.\\
\bottomrule
\end{tabular*}

@@

\begin{tabular*}{\columnwidth}[h]{rlrrl}
\toprule
\multicolumn{5}{c}{\textbf{50s: Stack, Memory, Storage and Flow Operations}} \vspace{5pt} \\
\textbf{Value} & \textbf{Mnemonic} & $\delta$ & $\alpha$ & \textbf{Description} \vspace{5pt} \\
0x50 & {\small POP} & 1 & 0 & Remove item from stack. \\
\midrule
0x51 & {\small DUP} & 1 & 2 & Duplicate stack item. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{M}_S[0]$ \\
\midrule
0x52 & {\small SWAP} & 2 & 2 & Exchange stack items. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{M}_S[1]$ \\
&&&& $\mathbb{M}'_T[1] \equiv \mathbb{M}_S[0]$ \\
\midrule
0x53 & {\small MLOAD} & 1 & 1 & Load word from memory. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{M}_M[\mathbb{M}_S[0] \dots (\mathbb{M}_S[0] + 32) ]$ \\
&&&& $\mathbb{M}'_i \equiv \max(\mathbb{M}_i, \ceil{ (\mathbb{M}_S[0] + 32) \div 32 })$ \\
\midrule
0x54 & {\small MSTORE} & 2 & 0 & Save word to memory. \\
&&&& $\mathbb{M}'_M[ \mathbb{M}_S[0] \dots (\mathbb{M}_S[0] + 32) ] \equiv \mathbb{M}_S[1]$ \\
&&&& $\mathbb{M}'_i \equiv \max(\mathbb{M}_i, \ceil{ (\mathbb{M}_S[0] + 32) \div 32 })$ \\
\midrule
0x55 & {\small MSTORE8} & 2 & 0 & Save byte to memory. \\
&&&& $\mathbb{M}'_M[ \mathbb{M}_S[0] ] \equiv (\mathbb{M}_S[1] \mod 256) $ \\
&&&& $\mathbb{M}'_i \equiv \max(\mathbb{M}_i, \ceil{ (\mathbb{M}_S[0] + 1) \div 32 })$ \\
\midrule
0x56 & {\small SLOAD} & 1 & 1 & Load word from storage. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{S}'[I_a]_{storage}[\mathbb{M}_S[0]]$ \\
\midrule
0x57 & {\small SSTORE} & 2 & 0 & Save word to storage. \\
&&&& $\mathbb{S}'[I_a]_{storage}[ \mathbb{M}_S[0] ] \equiv \mathbb{M}_S[1] $ \\
&&&& $c_{\text{\tiny SSTORE}} \equiv \begin{cases}
2G_{sstore} & \text{if} \quad \mathbb{M}_S[1] \neq 0 \; \wedge \; \mathbb{S}[I_a]_{storage}[\mathbb{M}_S[0]] = 0 \\
0 & \text{if} \quad \mathbb{M}_S[1] = 0 \; \wedge \; \mathbb{S}[I_a]_{storage}[\mathbb{M}_S[0]] \neq 0 \\
G_{sstore} & \text{otherwise}
\end{cases}$ \\
\midrule
0x58 & {\small JUMP} & 1 & 0 & Alter the program counter. \\
&&&& $J_{\text{\tiny JUMP}}(\mathbb{M}) \equiv \mathbb{M}_S[0] $ \\
&&&& This has the effect of writing said value to $\mathbb{M}_{pc}$. See section \ref{ch:model}. \\
\midrule
0x59 & {\small JUMPI} & 2 & 0 & Conditionally alter the program counter. \\
&&&& $J_{\text{\tiny JUMPI}}(\mathbb{M}) \equiv \begin{cases} \mathbb{M}_S[0] & \text{if} \quad \mathbb{M}_S[0] = 0 \\ \mathbb{M}_{pc} + 1 & \text{otherwise} \end{cases} $ \\
&&&& This has the effect of writing said value to $\mathbb{M}_{pc}$. See section \ref{ch:model}. \\
\midrule
0x5a & {\small PC} & 0 & 1 & Get the program counter. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{M}_{pc}$ \\
\midrule
0x5b & {\small MSIZE} & 0 & 1 & Get the size of active memory. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{M}_{i}$ \\
\midrule
0x5c & {\small GAS} & 0 & 1 & Get the amount of available gas. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{M}_{g}$ \\
\bottomrule
\end{tabular*}

@@

\begin{tabular*}{\columnwidth}[h]{rlrrl}
\toprule
\multicolumn{5}{c}{\textbf{f0s: System operations}} \vspace{5pt} \\
\textbf{Value} & \textbf{Mnemonic} & $\delta$ & $\alpha$ & \textbf{Description} \vspace{5pt} \\
0xf0 & {\small CREATE} & 5 & 1 & Create a new contract. \\
&&&& $\mathbf{b} \equiv \mathbb{M}_M[ \mathbb{M}_S[1] \dots (\mathbb{M}_S[1] + \mathbb{M}_S[2] - 1) ]$ \\
&&&& $\mathbf{i} \equiv \mathbb{M}_M[ \mathbb{M}_S[3] \dots (\mathbb{M}_S[3] + \mathbb{M}_S[4] - 1) ]$ \\
&&&& $(\mathbb{S}', \mathbb{M}'_g) \equiv \Lambda(\mathbb{S}^*, I_a, I_o, \mathbb{M}_g, I_p, \mathbb{M}_S[0], \mathbf{i}, \mathbf{b})$ \\
&&&& $\mathbb{S}^* \equiv \mathbb{S} \quad \text{except} \quad \mathbb{S}^*[I_a]_{nonce} = \mathbb{S}[I_a]_{nonce} + 1$ \\
&&&& $\mathbb{M}'_T[0] \equiv x$ \\
&&&& where $x=0$ if the code execution for this operation failed due to lack of gas;\\
&&&& $x=A(I_a, \mathbb{S}[I_a]_{nonce})$, the address of the newly created contract, otherwise. \\
&&&& $\mathbb{M}'_i \equiv \max(\mathbb{M}_i, \ceil{ \max(\mathbb{M}_S[1] + \mathbb{M}_S[2], \mathbb{M}_S[3] + \mathbb{M}_S[4]) \div 32 })$ \\
\midrule
0xf1 & {\small CALL} & 7 & 1 & Message-call into contract. \\
&&&& $\mathbf{i} \equiv \mathbb{M}_M[ \mathbb{M}_S[3] \dots (\mathbb{M}_S[3] + \mathbb{M}_S[4] - 1) ]$ \\
&&&& $\mathbf{o} \equiv \mathbb{M}_M[ \mathbb{M}_S[5] \dots (\mathbb{M}_S[5] + \mathbb{M}_S[6] - 1) ]$ \\
&&&& Let $g_k = \begin{cases}0 & \text{if} \quad \mathbb{M}_S[2] = 0 \\ \mathbb{M}_g - \min(\mathbb{M}_g, \mathbb{M}_S[2]) & \text{otherwise} \end{cases}$ \\
&&&& $(\mathbb{S}', g', \mathbf{o}) \equiv \Theta(\mathbb{S}, I_a, I_o, \mathbb{M}_S[0], g, I_p, \mathbb{M}_g - g_k, \mathbb{M}_S[1], \mathbf{i})$ \\
&&&& $\mathbb{M}'_g \equiv g' + g_k$ \\
&&&& $\mathbb{M}'_T[0] \equiv x$ \\
&&&& where $x=0$ if the code execution for this operation failed due to lack of gas;\\
&&&& $x=1$ otherwise. \\
&&&& $\mathbb{M}'_i \equiv \max(\mathbb{M}_i, \ceil{ \max(\mathbb{M}_S[3] + \mathbb{M}_S[4], \mathbb{M}_S[5] + \mathbb{M}_S[6]) \div 32 })$ \\
\midrule
0xf2 & {\small RETURN} & 2 & 0 & Halt execution returning output data. \\
&&&& $H_{\text{\tiny RETURN}}(\mathbb{M}) \equiv \mathbb{M}_M[ \mathbb{M}_S[0] \dots ( \mathbb{M}_S[0] + \mathbb{M}_S[1] - 1 ) ]$ \\
&&&& This has the effect of halting the execution at this point with output defined.\\
&&&& See section \ref{ch:model}. \\
&&&& $\mathbb{M}'_i \equiv \max(\mathbb{M}_i, \ceil{ (\mathbb{M}_S[0] + \mathbb{M}_S[1]) \div 32 })$ \\
\midrule
0xff & {\small SUICIDE} & 1 & 0 & Halt execution and obliterate account. \\
&&&& $\mathbb{S}'[\mathbb{M}_S[0]]_{balance} \equiv \mathbb{S}[\mathbb{M}_S[0]]_{balance} + \mathbb{S}[I_a]_{balance}$ \\
&&&& $\mathbb{S}'[I_a] \equiv \varnothing$ \\
\bottomrule
\end{tabular*}

@@

$0_{256}$ refers to the parent hash, a 256-bit hash which is all zeroes.

$0_{160}$ refers to the coinbase address, a 160-bit hash which is all zeroes.
